Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-02-25 article-models-tt.tex
small improvement

\begin{align}
& \inference{\jfam{\Gamma}{A}\qquad\jfam{\Gamma}{B}\qquad\jterm{\Gamma}{A}{x}}{\jfameq{\Gamma}{\subst{x}{\ctxwk{A}{B}}}{B}}\\
& \inference{\jfam{\Gamma}{A}\qquad\jfam{\ctxext{\Gamma}{B}}{Q}\qquad\jterm{\Gamma}{A}{x}}{\jfameq{\ctxext{\Gamma}{B}}{\subst{x}{\ctxwk{A}{Q}}}{Q}}\\
& \inference{\jterm{\Gamma}{A}{x}\qquad\jterm{\Gamma}{B}{y}}{\jtermeq{\Gamma}{B}{\subst{x}{\ctxwk{A}{y}}}{y}}\\
& \inference{\jterm{\Gamma}{A}{x}\qquad\jterm{\ctxext{\Gamma}{B}}{Q}{g}}{\jtermeq{\ctxext{\Gamma}{B}}{Q}{\subst{x}{\ctxwk{A}{g}}}{g}}
\end{align}

Using the rules of the compatibility of substitution with weakening and of the
compatibility of weakening with itself, we see that we can show
\begin{equation*}
\jfameq{\Gamma}{\subst{f}{\ctxwk{\Gamma}{{\Delta}{\greek{E}}}}}{\ctxwk{\Gamma}{E}}
\end{equation*}
for any three contexts $\Gamma$, $\Delta$ and $\greek{E}$ and any $\jhom{\Gamma}{\Delta}{f}$.
It follows that for $\jhom{\Delta}{\greek{E}}{g}$ we have
\begin{equation*}
\jhom{\Gamma}{\greek{E}}{\subst{f}{\ctxwk{\Gamma}{g}}}
\end{equation*}
The term $\jcomp{\Gamma}{f}{g}$ is the composition of $g$ with $f$. We may call
a term $\jhom{\Gamma}{\Delta}{f}$ a morphism from $\Gamma$ to $\Delta$.

>>>>

\begin{align}
& \inference{\jfam{\Gamma}{A}\qquad\jfam{\Gamma}{B}\qquad\jterm{\Gamma}{A}{x}}{\jfameq{\Gamma}{\subst{x}{\ctxwk{A}{B}}}{B}}\\
& \inference{\jterm{\Gamma}{A}{x}\qquad\jterm{\Gamma}{B}{y}}{\jtermeq{\Gamma}{B}{\subst{x}{\ctxwk{A}{y}}}{y}}\\
& \inference{\jfam{\Gamma}{A}\qquad\jfam{\ctxext{\Gamma}{B}}{Q}\qquad\jterm{\Gamma}{A}{x}}{\jfameq{\ctxext{\Gamma}{B}}{\subst{x}{\ctxwk{A}{Q}}}{Q}}\\
& \inference{\jterm{\Gamma}{A}{x}\qquad\jterm{\ctxext{\Gamma}{B}}{Q}{g}}{\jtermeq{\ctxext{\Gamma}{B}}{Q}{\subst{x}{\ctxwk{A}{g}}}{g}}
\end{align}

Using the rules of the compatibility of substitution with weakening and of the
compatibility of weakening with itself, we see that we can show
\begin{equation*}
\jfameq{\ctxext{\Gamma}{A}}{\subst{f}{\ctxwk{A}{{B}{C}}}}{\ctxwk{A}{C}}
\end{equation*}
for any three families $A$, $B$ and $C$ in context $\Gamma$ and any $\jterm{\ctxext{\Gamma}{A}}{\ctxwk{A}{B}}{f}$.
It follows that for $\jterm{\ctxext{\Gamma}{B}}{\ctxwk{B}{C}}{g}$ we have
\begin{equation*}
\jterm{\ctxext{\Gamma}{A}}{\ctxwk{A}{C}}{\subst{f}{\ctxwk{A}{g}}}
\end{equation*}
The term $\jcomp{A}{f}{g}$ is the composition of $g$ with $f$. We may call
a term $\jterm{\ctxext{\Gamma}{A}}{\ctxwk{A}{B}}{f}$ a morphism from $A$ to $B$.
